Nucleotide Diversity Loss on a Plant Y Chromosome Following Recent Recombination Suppression

### 2016-12-19 code/R/Nov25_2016.Rmd
organization; new edits up to Methods

plot(c(tx_x_auto/0.75,XA_0.6/0.75, xa_given_y/0.75),
        ylim=c(0,1.5),
        ylab="X/A relative to neutral model", main="X/A for a sex ratio of 0.6", 
        xlab="expected                                                      observed")
curve((1/(8*x))/0.25, from=0.5, to=1, lwd=2, add=T)
abline(lty=2,h=1.13)
abline(lty=2,h=0.0004)

@@

xa_given_y=0.0003 # y theta * 3
ya_given_x=0.00156 #x theta * 1/3
XA=c(tx_x_auto, XA_0.5, XA_0.6, XA_0.7, XA_0.8, XA_0.9)
YA=c(tx_y_auto, YA_0.5, YA_0.6, YA_0.7, YA_0.8, YA_0.9)
ChrRatios=cbind(XA,YA)

@@

```{r}
#0.25*(exp(-(0.02/((2*0.002)+0)))
bgs_exp=0.00168449

barplot(c(tx_y_auto,ya_given_x,bgs_exp), ylim=c(0,0.04), col="gray52", ylab="Y/A",
        names.arg=c("observed", "predicted from X", "predicted by bgs"), cex.names=0.75)
segments(x0=0.7,y0=0.01,x1=0.7,y1=0.04,lwd=0.75)
arrows(x0=0.7,y0=0.01,x1=0.7,y1=0.04,lwd=0.75,angle = 90, code = 3, length = 0.04)

>>>>

```{r}
xa_given_y=0.0003 # y theta * 3
ya_given_x=0.00156 #x theta * 1/3
plot(c(tx_x_auto/0.75,XA_0.6/0.75, xa_given_y/0.75),
        ylim=c(0,1.5),
        ylab="X/A relative to neutral model", main="X/A for a sex ratio of 0.6", 
        xlab="expected                                                      observed")
curve((1/(8*x))/0.25, from=0.5, to=1, lwd=2, add=T)
abline(lty=2,h=1.13)
abline(lty=2,h=0.0004)

@@

XA=c(tx_x_auto, XA_0.5, XA_0.6, XA_0.7, XA_0.8, XA_0.9)
YA=c(tx_y_auto, YA_0.5, YA_0.6, YA_0.7, YA_0.8, YA_0.9)
ChrRatios=cbind(XA,YA)

@@

```{r}
#0.25*(exp(-(0.02/((2*0.002)+0)))
#bgs_exp=0.00168449

BGS_YA=0.0054
SEXRATIO_YA=YA_0.6
OBS_YA=0.018

#barplot(c(OBS_YA/YA_0.6,BGS_YA/YA_0.6), ylim=c(0,0.2), col="gray52", ylab="Y/A ratio relative to the neutral prediction",
#        names.arg=c("observed", "BGS theory prediction"), cex.names=0.75)
#segments(x0=0.7,y0=0.009/YA_0.6,x1=0.7,y1=0.03/YA_0.6,lwd=0.75)
#arrows(x0=0.7,y0=0.009/YA_0.6,x1=0.7,y1=0.035/YA_0.6,lwd=0.75,angle = 90, code = 3, length = 0.04)

par(las=1)
barplot(c(OBS_YA/YA_0.6,BGS_YA/YA_0.6), ylim=c(0,0.2), col="gray52",ylab=expression(paste(pi/pi[0])),
        names.arg=c("observed", "BGS theory"), cex.names=0.75)
segments(x0=0.7,y0=0.009/YA_0.6,x1=0.7,y1=0.035/YA_0.6,lwd=0.75)
arrows(x0=0.7,y0=0.009/YA_0.6,x1=0.7,y1=0.035/YA_0.6,lwd=0.75,angle = 90, code = 3, length = 0.04)
